---
title: "TMS motor-evoked potentials with PhysioNeurophys"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TMS motor-evoked potentials with PhysioNeurophys}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

PhysioNeurophys analyses transcranial magnetic stimulation (TMS) and peripheral
motor neurophysiology on `PhysioExperiment` objects: motor-evoked-potential (MEP)
amplitude and latency, Boltzmann recruitment curves, H-reflex and F-wave
metrics, paired-pulse SICI/ICF, cortical silent period, TMS-EEG cleaning, and the
PREP2 prognosis algorithm.

This vignette uses the built-in simulator so it runs offline. TEP/MEP labels are
measurement windows, not proof of a cortical source.

```{r setup}
library(PhysioNeurophys)
```

## 1. Simulate epoched MEPs

`make_mep()` generates biphasic MEP waveforms with a known latency and a
Boltzmann amplitude-intensity relationship, and attaches the per-trial TMS pulse
metadata. Epochs start 20 ms before the pulse.

```{r simulate}
pe <- make_mep(n_trials = 12, seed = 1)
dim(SummarizedExperiment::assay(pe))   # samples x channels x trials
getTMSpulses(pe)[1:3, ]
```

## 2. MEP amplitude

Peak-to-peak amplitude is measured within a response window, per channel and
trial. Pass `epoch_start_ms = -20` to match the simulated epoch.

```{r amplitude}
amp <- mepAmplitude(pe, epoch_start_ms = -20)
head(amp[, c("trial", "intensity_pct_mso", "p2p")])
```

## 3. MEP onset latency

```{r latency}
lat <- mepLatency(pe, epoch_start_ms = -20)
head(lat[, c("trial", "onset_sample", "latency_ms")])
```

## 4. Boltzmann recruitment curve

Amplitude rises sigmoidally with stimulator intensity. `recruitmentCurve()` fits
a three-parameter logistic and returns the fitted parameters and fit quality.

```{r recruitment}
rc <- recruitmentCurve(pe, epoch_start_ms = -20)
rc
```

## Where to go next

`?PhysioNeurophys` lists every entry point, including peripheral measures
(`hReflexRecruitment()`, `hMaxMMax()`, `fWaveDetect()`), paired-pulse
inhibition/facilitation (`pairedPulse()`, `siciIcf()`), the cortical silent
period (`corticalSilentPeriod()`), TMS-EEG pulse removal and cleaning
(`removeTMSpulse()`, `tmsSSPSIR()`, `soundClean()`, `tepAverage()`), and the
PREP2 upper-limb prognosis (`prep2()`).
